Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{{DISTRIBUTION STATEMENT A. Approved for public release.} }

### 2021-05-14 paper/agree.tex
Fix typos

We claim that a synthesized high-assurance component preserves the input to output
relationship in the specification $s$ over every stream in $\mathcal{L}(s)$. 
Let $\pi^\prime
= \konst{SynthEval}\ s\ \pi$ denate a function that synthesizes $s$ and then
evaluates that synthesized component on the stream $\pi$ to create a new
stream $\pi^\prime$ containing added output and other bindings. We
say that two streams, $\pi_a = \pi_b$ are equivalent in regards to a
specification $s$ if and only if the two streams are the same length and
agree on bindings for the input and output for $s$ at every step of the streams.
We now formally state the correctness claim for synthesis.
%
\[
  \forall \pi \in \mathcal{L}(s)\ ((\konst{SynthEval}\ s\ I_s(\pi)) =_s \pi)\\
\]
%
where $I_s(\pi)$ returns the corresponding stream that only retains bindings
for inputs in each step and nothing else. The claim is that the synthesized component
generates the same output stream as the specification for any stream
belonging to the specification that is restricted to just input binding at each step.

>>>>

We claim that a synthesized high-assurance component preserves the input to output
relationship in the specification $s$ over every stream in $\mathcal{L}(s)$. 
Let $\pi^\prime
= \konst{SynthEval}\ s\ \pi$ denote a function that synthesizes $s$ and then
evaluates that synthesized component on the stream $\pi$ to create a new
stream $\pi^\prime$ containing added output and other bindings. We
say that two streams are equivalent in regards to a
specification, denoted as $\pi =_s \pi^\prime$, if and only if the two streams are the same length and
agree on bindings for the input and output for $s$ at every step of the streams.
We now formally state the correctness claim for synthesis.
%
\[
  \forall \pi \in \mathcal{L}(s)\ ((\konst{SynthEval}\ s\ I_s(\pi)) =_s \pi)\\
\]
%
where $I_s(\pi)$ returns the corresponding stream that only retains bindings
for inputs in each step and nothing else. The claim is that the synthesized component
generates the same output stream as the specification for any stream
belonging to the specification that is restricted to just input bindings at each step.
